\section{Main Functionalities}
%What are the main functionalities of the web app? what services does it offer and how it is organized?

The web application is tailored to enhance user engagement with the movie catalog, offering a seamless experience for exploring, rating, and interacting with movies. Users can delve into the extensive movie collection, rate films, share their opinions through comments, curate personalized lists of favorite movies, and access detailed information about the cast and crew, thereby eliminating the need to visit multiple sources or cinemas.
The website is structured into four key areas:
 \begin{itemize}
\item \textbf{Public Area:} Accessible to all users, the homepage serves as a gateway to the movie collection, showcasing top-rated films and providing an overview of the available titles.
\item \textbf{User Area:} Users have access to a range of functionalities, including the ability to:
\begin{itemize}
\item Can register the website if they are not registered. 
\item Update their personal information.
\item Explore movies through various options, such as watchlists and awards, and access general movie details.
\item Browse and contribute movie reviews, sharing their insights and opinions.
\item Manage their watchlists by adding or removing movies based on their preferences.
\end{itemize}
\item \textbf{Movie Area:} This section offers a comprehensive repository of movie-related information, including:
\begin{itemize}
\item Detailed movie profiles featuring essential details like title, director, and cast.
\item Opportunities for users to read existing reviews and submit their own, fostering a community-driven discussion around films.
\item Convenient options for users to add movies to their watchlists for future reference and viewing.
\end{itemize}
\item \textbf{Person Area:} Dedicated to providing insights into the individuals behind the scenes, this area offers:
\begin{itemize}
\item Detailed profiles of actors/actresses, directors, writers and producers, showcasing their career highlights and contributions to the film industry.
\item Information about awards they have received for their work across various films, highlighting their achievements and recognition.
\item A curated list of films in which they have played a significant role, offering users a deeper understanding of their filmography and artistic journey.
\end{itemize}
\item \textbf{Admin Area:} 
The admin area is a web interface where the application owner manages movies, actresses, actors, directors, and related content. It allows adding, updating, and removing information about actresses, movie descriptions, actor details, and director profiles.
\end{itemize}